ChemKED: a human- and machine-readable data standard for chemical kinetics experiments

### 2017-02-25 pyked.tex
Rework installation instructions

\pk{} is available under the permissive, open-source BSD 3-clause license via a GitHub
repository: \url{https://github.com/pr-omethe-us/PyKED}. It can be installed using setuptools
by downloading the source code files and executing \texttt{python setup.py install}. More mature
versions of \pk{} will be distributed on \href{https://pypi.python.org/pypi}{PyPI}
(Python Package Index) and conda-forge.\todo{add URL}{}

%====================================================================
\section{Use example}
%
\todo[inline]{Bryan/Kyle to do}
\todo[inline]{Idea: CONV simulations using Cantera in a loop with conditions
from the Pandas output for butanol?}
\todo[inline]{Idea: VPRO simulations using Cantera from a \ck{} file for an RCM
datapoint}

>>>>

\pk{} is licensed under the permissive, open-source BSD 3-clause license. The
source code is publicly available on GitHub at
\url{https://github.com/pr-omethe-us/PyKED}. Installation of stable versions can
be accomplished from a package repository, using either \python|pip| to install
from \href{https://pypi.python.org/pypi}{PyPI} (Python Package Index), or
\python|conda| to install from the
\href{https://anaconda.org/conda-forge}{\texttt{conda-forge}} channel. In
addition, \pk{} can be installed from the source code by running \python|python
setup.py install| or \python|pip install .| from the root directory of the
repository.

%====================================================================
\section{Usage example}\label{sec:usage-example}
%
\todo[inline]{Bryan/Kyle to do}
\todo[inline]{Idea: CONV simulations using Cantera in a loop with conditions
from the Pandas output for butanol?}
\todo[inline]{Idea: VPRO simulations using Cantera from a \ck{} file for an RCM
datapoint}
